Heuristics for the Score-Constrained Strip-Packing Problem

### 2018-03-21 PAPER/main.tex
changed to use elsarticle class
added spaces between definitions

\documentclass[oribibl]{llncs}

@@

\title{Heuristics for the Score-Constrained Strip-Packing Problem}
\author{Asyl L. Hawa \and Rhyd M. R. Lewis \and Jonathan M. Thompson}
\institute{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
\date{\today}

\begin{document}
\maketitle

@@

@@

Firstly, let us introduce the Constrained Pair-Ordering Problem:

\begin{definition}
	\label{defn:cpop}
	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple. The Constrained Pair Ordering Problem (CPOP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
	\begin{equation}
		\label{eqn:cpop}
		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
	\end{equation}
	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the vicinal sum constraint.
\end{definition}

@@

Observe that, in this particular strip-packing problem, the widths of the individual items are not taken into account, since the aim is to arrage the items onto a strip of seemingly infinite length. In reality, strips of material are provided in fixed lengths. Given a large problem instance, multiple strips may be required to feasibly accommodate all of the items. For this reason, we define a new problem to be investigated.

@@

The following definition describes a variant of the classical Hamiltonian cycle on a graph $G$.

\begin{definition}
	\label{defn:althamcycle}
	Let $G(V, P\cup E)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $E$. $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such successive edges alternate between sets $P$ and $E$. For example, if $(v_{i-1}, v_i) \in P$, then $(v_i, v_{i+1}) \in E$, or vice versa.
\end{definition}

\begin{theorem}
	\label{thm:cpopsoln}
	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the CPOP if and only if its corresponding graph $G(V, P\cup E)$ contains an alternating Hamiltonian cycle.
\end{theorem}
\begin{proof}
	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices. By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $P$. Thus, there exists a set of $n+1$ edges from $E$ that, together with the edges in $P$, form the alternating Hamiltonian cycle. Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $P$. The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple. \textcolor{OrangeRed}{edges E vicinal sum constraint equation 2}. \qed
\end{proof}

@@

>>>>

\documentclass[preprint]{elsarticle}

@@

\begin{document}

\begin{frontmatter}
\title{Heuristics for the Score-Constrained Strip-Packing Problem}
\author{Asyl L. Hawa}
\author{Rhyd Lewis}
\author{Jonathan M. Thompson}
\address{School of Mathematics, Cardiff University, Senghennydd Road, Cardiff, UK, CF24 4AG}
\date{\today}

%\maketitle

@@

\end{frontmatter}

@@

Firstly, let us introduce the Constrained Pair-Ordering Problem:\\

\begin{definition}
	\label{defn:cpop}
	Let $\mathcal{M}$ be a multiset of unordered pairs of positive integers $\mathcal{M} = \{\{a_1, b_1\}, \{a_2,b_2\},...,\{a_n,b_n\}\}$, and let $\mathcal{T}$ be an ordering of the elements of $\mathcal{M}$ such that each element is a tuple. The Constrained Pair-Ordering Problem (CPOP) consists of finding a solution $\mathcal{T}$ such that, given a fixed value $\tau \in \mathbb{Z}^{+},$
	\begin{equation}
		\label{eqn:cpop}
		\textup{\textbf{rhs}}(i) + \textup{\textbf{lhs}}(i+1) \geq \tau \hspace{5mm} \forall \hspace{1mm} i \in \{1,2,..., n-1\},
	\end{equation}
	where \textup{\textbf{lhs}($i$)} and \textup{\textbf{rhs}($i$)} denote the left- and right-hand values of the $i$th tuple. The inequality is referred to as the vicinal sum constraint.
\end{definition}

@@

Observe that, in this particular strip-packing problem, the widths of the individual items are not taken into account, since the aim is to arrage the items onto a strip of seemingly infinite length. In reality, strips of material are provided in fixed lengths. Given a large problem instance, multiple strips may be required to feasibly accommodate all of the items. For this reason, we define a new problem to be investigated. \\

@@

The following definition describes a variant of the classical Hamiltonian cycle on a graph $G$.\\

\begin{definition}
	\label{defn:althamcycle}
	Let $G(V, P\cup E)$ be an undirected graph, where each edge is a member of one of two sets, $P$ or $E$. $G$ contains an alternating Hamiltonian cycle if there exists a Hamiltonian cycle such successive edges alternate between sets $P$ and $E$. For example, if $(v_{i-1}, v_i) \in P$, then $(v_i, v_{i+1}) \in E$, or vice versa.\\
\end{definition}

\begin{theorem}
	\label{thm:cpopsoln}
	There exists a feasible solution $\mathcal{T}$ to an instance $\mathcal{M}$ of the CPOP if and only if its corresponding graph $G(V, P\cup E)$ contains an alternating Hamiltonian cycle.
\end{theorem}
\begin{proof}
	Let $\mathcal{A} = \{v_1, v_2, ..., v_{2n+1}, v_{2n+2}\}$ be an alternating Hamiltonian cycle on $G$, where $v_{2n+1}$ and $v_{2n+2}$ are the dominating vertices. By definition, $\mathcal{A}$ contains all vertices on $G$, and all $n+1$ edgs in $P$. Thus, there exists a set of $n+1$ edges from $E$ that, together with the edges in $P$, form the alternating Hamiltonian cycle. Now, removing the dominating vertices and any incident edges gives rise to an alternating Hamiltonian path $\mathcal{A}' = \{v_1, v_2, ..., v_{2n-1}, v_{2n}\}$, whose first edge $(v_1, v_2)$ and last edge $(v_{2n-1}, v_{2n})$ are in $P$. The order of the values corresponding to each vertex of this path form a feasible solution $\mathcal{T}$, where values that are partners make up a tuple. \textcolor{OrangeRed}{edges E vicinal sum constraint equation 2}.
\end{proof}

@@

\section*{References}
